---
title: "Fixed Effects Estimation"
author: "Balachandar & Mohammed"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Panel Data Analysis with R

## 1. Set working directory

## 2. Load the library

library(plm)
library(knitr)
library(broom)
library(tidyverse)
library(stargazer)
library(lmtest)
library(gplots)
library(foreign)

## 3. Import Dataset (STATA version)
# Rental Data from Wooldridge

RENTAL <- read.dta("RENTAL.DTA")

#  Indexed by city and year

rental_p <- pdata.frame(RENTAL, index=c("city", "year"))

## 4. Display the data

str(RENTAL)
str(rental_p)
head(RENTAL)
head(rental_p)

#  Model lrent~y90+lpop+lavginc+pctstu

## 5. OLS using lm

ols <- lm(lrent~y90+lpop+lavginc+pctstu, RENTAL)
summary(ols)


## 6. OLS using plm

pooled <- plm(lrent~y90+lpop+lavginc+pctstu, data=RENTAL, model="pooling", index=c("city", "year"))
summary(pooled)

#OR use this format

pooled2 <- plm(lrent~y90+lpop+lavginc+pctstu, data=rental_p, model="pooling")

summary(pooled2)


## Results table

stargazer(pooled, pooled2, type ="text")

## 7. Test for heteroscedasticity

res <- residuals(ols)
yhat <- fitted(ols)

plot(RENTAL$pctstu, res, xlab = "%Students", ylab = "Residuals")
plot(yhat, res,  xlab = "%Students", ylab = "Residuals" )

## 8. Fixed Effects

# Includes within-entity effects
```{r}
fe <- plm(lrent~y90+lpop+lavginc+pctstu, data=rental_p, model="within")
summary(fe)
# Show fixed effects for all 64 cities
fixef(fe)
````


## 9. Test for FE vs OLS
# Ho: OLS is better than FE, reject at p < 0.05
```{r}
pFtest(fe, ols)
stargazer(fe, type = "text")
```
## 10. Random Effects

# Includes both the within-entity and between-entity effects
```{r}
re <- plm(lrent~y90+lpop+lavginc+pctstu, data=rental_p, model="random")
summary(re)
```
## 11. FE VS RE

## Hausman Test Ho: RE is preferred, Ha: FE is preferred (p < 0.05)
```{r}
phtest(fe, re)
```
# Beautify / Tabulate result
```{r}
kable(tidy(phtest(fe, re)))
````
## 12. Breusch Pagan Lagrange Multiplier Test Ho: No panel effect, i.e., OLS is better. Ha: RE is better at p <0.05

```{r}
plmtest(pooled, type = c("bp"))

#plmtest(ols, type=c("bp")) - use PLM package
```

## 13. Test for cross-sectional dependence [NOTE: Suitable only for macro panels with long time series] [Not suitable for RENTAL dataset]
# Breusch-Pagan LM test of independence and Pasaran CD test, Ho: There is no cross-sectional dependence
```{r}
pcdtest(fe, test = c("lm"))
pcdtest(fe, test = c("cd"))
```


## 14. Testing for serial correlation [NOTE: Suitable only for macro panels with long time series] [Not suitable for RENTAL dataset]
# Ho: There is no serial correlation
```{r}
pbgtest(fe)
```

## 15. Breusch - Pagan test for heteroscedasticity Ho: Homoscedasticity Ha: Heteroscedasticity

```{r}  
bptest(lrent ~ y90+lpop+lavginc+pctstu+factor(city), data=rental_p, studentize = F)
```
